CTCF threshold analysis

### 2022-07-01 manuscript/manuscript.Rmd
Reorder authors

Douglas Phanstiel  
Eric Davis  
Michael Love  
Mikhail Dozmorov  
Stuart Lee  
Tim Triche  
Wancen Mu

@@

**Table 1. CTCF PWM information.** "Motif" - individual motif IDs or the total number of motifs per database; "Length" - motif length of the range of lengths; "URL" - direct links to motif pages; "Ref" - literature reference.
```{r eval=FALSE}
fileNameIn1 <- file.path(dir_data, "Tables", "Table_1_PWMs.xlsx")
mtx <- read_xlsx(fileNameIn1)
mtx[is.na(mtx)] <- ""
kable(mtx)
```

>>>>

Mikhail Dozmorov *  
Wancen Mu  
Eric Davis  
Stuart Lee  
Tim Triche  
Douglas Phanstiel  
Michael Love

@@

**Table 1. CTCF PWM information.** "Motif" - individual motif IDs or the total number of motifs per database; "Length" - motif length of the range of lengths; "URL" - direct links to motif pages; "Ref" - literature reference.
```{r eval=TRUE}
fileNameIn1 <- file.path(dir_data, "Tables", "Table_1_PWMs.xlsx")
mtx <- read_xlsx(fileNameIn1)
mtx[is.na(mtx)] <- ""
kable(mtx)
```
